Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-10-26 R Journal/beger-hill-metternich-minhas-ward.tex
revisions and memo complete

Underlying both plotting functions is the \code{predict} function, which
can be used on an object of class \code{spdur} to generate several kinds
of predictions, including the probability that an observation is
``at-risk'' and the probability of failure for a given time period.

>>>>

Underlying both plotting functions is the \code{predict} function, which
can be used on an object of class \code{spdur} to generate several kinds
of predictions, including the probability that an observation is
``at-risk'' and the probability of failure for a given time period. By default 
\code{predict} calculates the conditional hazard, but the probability that an 
observation is at risk may also be of interest. These models 
are most appropriate in cases where there is a strong theoretical reason to suspect 
some units are not at risk, as in the canonical applications (not everyone smokes, 
some cancer patients are cured, some convicts do not relapse, etc.). Whether 
an observation is cured or at-risk is ultimately unknowable, but estimating cure probabilities 
can give users some idea of whether a split-population model is appropriate 
for their application. Here we use \code{predict} to estimate conditional cure 
probabilities from the Weibull model.

\begin{example}
  bscoup$ccure_prob <- predict(weib_model, type = "conditional cure", 
  +    newdata = bscoup, na.action = "na.exclude")
  mean(bscoup$ccure_prob, na.rm = TRUE)
  [1] 0.4333912
\end{example}
